---
title       : Shiny Water Explorer Pitch 
subtitle    : 
author      : Maksim Pecherskiy
job         : 
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Shiny Water Explorer Pitch 
### Maksim Pecherskiy
#### September 26, 2015

---

## Purpose
* Residents from different neighborhoods consume water in different amounts.
* Show where the top X% of water consumers are living.
* Show which neighborhoods consume the most water.


---

## Assumptions To Be Mitigated  
* Data used is a small sample.
* Not adjusted for multi-tenant buildings
* Not adjusted for businesses
* Areas differ in demographics and weather patterns - comparing **just** on consumptions is incomplete.
* Areas differ in acreage size (next slide)

---

## Area Acreages

```{r echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
library(dplyr) 
library(rgdal) 
library(ggplot2)

# Load SHP
com_plan <- readOGR("./data/shp/community_plan_sd",
    layer = "community_plan_sd")
```
```{r echo=TRUE,message=FALSE,warning=FALSE}

g <- ggplot(data = com_plan@data, aes(x = cpname, y = acreage)) +
          geom_bar(stat="identity") + coord_flip() + xlab("Neighborhood") +
          ylab("Acreage")
print(g)
```

---
## Next Steps
* Provide more controls for smarter analysis of water usage
* Filter for multi-tenant
* Filter for residential
* Bring in weather data
* Adjust for acreage of area


